Final paper detail checks and analyses

### 2021-01-07 Final_analyses_checks_notebook.Rmd
added frequency tables

```{r read in data } 
# Read in data
library(tidyverse)
library(data.table)
library(lubridate)
library(psych)

@@

```{r most recent sign up}

max(RAMP.prepan$startDate.coping)
max(GLAD.prepan$startDate.coping)
max(NBR.prepan$startDate.coping)

@@

## Means, SD and n

### overall

>>>>

```{r read in data } 
# Read in data
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)

@@

```{r most recent sign up}
print("RAMP")
max(RAMP.retro$startDate.coping)
print("GLAD")
max(GLAD.retro$startDate.coping)
print("NBR")
max(NBR.retro$startDate.coping)

@@

## Sample sizes

## frequencies (retrodemic dataset)

### pandemic change gad

```{r retro freq table gad perceived change}
dat.retro %>%
  group_by(Sample) %>%
  freq(gad.pandemic_felt_feelings)

```
### pandemic change phq

```{r retro freq table phq perceived change}

dat.retro %>%
  group_by(Sample) %>%
  freq(phq.pandemic_felt_feelings)

### Ethnicity
```{r retro freq table ethnicity}
dat.retro %>%
  group_by(Sample) %>%
  freq(Ethnicity_collapsed) 
```
### Gender
```{r retro freq table gender}
dat.retro %>%
  group_by(Sample) %>%
  freq(Gender_collapsed) 
```
### age categorical
```{r retro freq table age collapsed}
dat.retro %>%
  group_by(Sample) %>%
  freq(age_category_collapsed) 
```
### Employment

```{r retro freq table employment collapsed}
dat.retro %>%
  group_by(Sample) %>%
  freq(employment_prior_covid) 
```

### anxiety disorders
```{r retro freq table diagnosis anxiety}
dat.retro %>%
  group_by(Sample) %>%
  freq(anxiety_disorders) 
```

### Depressive disorders
```{r retro freq table diagnosis depression}
dat.retro %>%
  group_by(Sample) %>%
  freq(depressive_disorders) 
```
### Depression and anxiety
```{r retro freq table diagnosis depression and anxiety}
dat.retro %>%
  group_by(Sample) %>%
  freq(depression_and_anxiety) 
```
### Eating disorders
```{r retro freq table diagnosis eating disorder}
dat.retro %>%
  group_by(Sample) %>%
  freq(eating_disorders)

```
### OCD
```{r retro freq table diagnosis obsessive compulsive disorders}
dat.retro %>%
  group_by(Sample) %>%
  freq(obsessive_compulsive_disorders)

### Psychosis
```{r retro freq table diagnosis psychotic disorders}
dat.retro %>%
  group_by(Sample) %>%
  freq(psychotic_disorders)

### Bipolar
```{r retro freq table diagnosis bipolar}
dat.retro %>%
  group_by(Sample) %>%
  freq(mhd.mania_hypomania_bipolar_or_manicdepression)

### PTSD
```{r retro freq table diagnosis PTSD}
dat.retro %>%
  group_by(Sample) %>%
  freq(mhd.posttraumatic_stress_disorder_ptsd)

### ASD

```{r retro freq table diagnosis ASD}
dat.retro %>%
  group_by(Sample) %>%
  freq(autism_spectrum_disorder)

### ADHD
```{r retro freq table diagnosis ADHD}
dat.retro %>%
  group_by(Sample) %>%
  freq(mhd.attention_deficit_hyperactivity_disorder)

### Personality disorders
```{r retro freq table diagnosis personality disorder}
dat.retro %>%
  group_by(Sample) %>%
  freq(mhd.personality_disorder)

### Controls 
```{r retro freq table diagnosis control}
dat.retro %>%
  group_by(Sample) %>%
  freq(control) 
```

### Dont know or prefer not to say
```{r retro freq table diagnosis prefer not to say}
dat.retro %>%
  group_by(Sample) %>%
  freq(DidNotRespondMHD) 
```

## Means, SD and n
### overall
